---
output: 
  html_document:
    toc: true
    number_sections: true
published: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here's a quick guide on connecting to SQL Server from R using the `RODBC` package. In saying that, make sure you have `RODBC` package installed by going:

```{r}
require(RODBC)
```

If you don't see the loading message above, install the package from CRAN:

```{r, eval=FALSE}
install.packages("RODBC")
```

# Set up the connection

Assuming the machine you're on already has a System Data Source configured within the ODBC Data Source Administrator. This should be the case if the SQL Server uses Windows Authentication.

```{r, eval=FALSE}
con <- odbcConnect("DSNName")
```

If you use a username - password combination to log in, do this instead:

```{r, eval=FALSE}
con <- odbcConnect("DatabaseName", uid = "user", pwd = "pass")
```


# Build your query

Insert your query into a string. Note that you can do more than just the `SELECT` keyword.

```{r, eval=FALSE}
query <- "SELECT * FROM db.schema.tablename"
```

# Execute your query

Execute your query with the `sqlQuery` function. You can save the results to an object so you can do stuff with it. If you don't the results will just be printed in the console for you.

```{r, eval=FALSE}
# query printed to console
sqlQuery(con, query)
# query saved to data object
data <- sqlQuery(con, query)
```

# Close your connection

Once you've retrieved the data you need, it is good practice to close the connection.

```{r, eval=FALSE}
close(con)
```

# Do stuff to your data

Congratulations, you can now do stuff to your data :)